DATA 605 Week 13

### 2019-04-27 DATA605/MSilva_Assign13.Rmd
Completed Assignment 13

---
title: "DATA 605 Week 13"
author: "Mike Silva"
date: "April 23, 2019"
output: 
  rmdformats::readthedown:
    highlight: kate
---

## Question 1
**Use integration by substitution to solve the integral below.**

@@

$$\int_{-1}^4{(x+2)-(x^2-2x-2)} \rightarrow (x^2+2x)-(\frac{x^3}{3}+x^2-2x)|_{-1}^4$$

@@

@@

$$\int{ln(9x) \times x^6 dx}$$

@@

>>>>

---
title: "DATA 605 Week 13"
author: "Mike Silva"
date: "April 23, 2019"
output: html_document
---

## Question 1

**Use integration by substitution to solve the integral below.**

@@

  $$\int_{-1}^4{(x+2)-(x^2-2x-2)} $$

@@

I am assuming sales are uniform throughout the year (no seasonality).  I am also assuming that there is no lag between ordering and receiving the items.  I am also assumuing that the orders will be for the same lot size.  I am also assuming that I am starting with zero irons in inventory on day one.

Total costs are the sum of the carrying/holding costs (H(x)) and the reordering costs(R(x)).

$$H(x) =  3.75 \times \frac{x}{2} \rightarrow H(x) = 1.875x$$
and

$$R(x) = 8\times\frac{110}{x}\rightarrow R(x)=\frac{880}{x}$$

So total costs as a function is:

$$C(x) = 1.875x + \frac{880}{x}$$

We will take the first derivative and set it equal to zero and solve for x to find the number of orders to minimize the costs.

$$C'(x) =1.875 - \frac{880}{x^2}$$

$$0 =1.875 - \frac{880}{x^2}$$

$$-1.875 = - \frac{880}{x^2}$$

$$-1.875 x^2= - 880$$

$$x^2 = \frac{-880}{-1.875}$$

$$x = \sqrt{\frac{880}{1.875}} = 21.6641 $$
**The costs are minimized at 22 orders with 5 irons per order**

The blue line in the following graph is the cost function and the red point is where it is minimized.

```{r, echo=FALSE}
library(ggplot2)
get_costs <- function(x){
  return(1.875 * x + (880 / x))
}

df <- data.frame(orders = 1:110, costs = get_costs(1:110))
m <- df[df$costs == min(df$costs),]

ggplot(data = data.frame(x = 0), mapping = aes(x = x)) +
  stat_function(fun = get_costs, color="blue") + 
  xlim(0, 110) +
  ylim(0, 1000) + 
  geom_point(x=m$orders, y=m$costs, color="red") +
  geom_hline(yintercept = 0, color="black") +
  geom_vline(xintercept = 0, color="black") +
  xlab("Orders") +
  ylab("Total Costs") +
  theme(aspect.ratio=1)
```

@@

$$\int{ln(9x) x^6 dx}$$

The integration by part formula is

$$\int{f(x)g'(x)}=f(x)g(x)-\int{f'(x)g(x)}$$

Let $f(x) = ln(9x)$ and let $g'(x) = x^6$.  $f'(x)=\frac{1}{x}$ and $g(x) = \int{x^6}=\frac{x^7}{7}$.

Substituting

$$ln(9x)x^6- \int{\frac{1}{x}\frac{x^7}{7} }$$

Evaluating the sub-integral

$$\int{\frac{1}{x}\frac{x^7}{7}} = \int{\frac{x^6}{7}} = \frac{x^7}{49}$$

$$ln(9x)x^6- \frac{x^7}{49}$$

@@

If it is a PDF then

$$F(x) = \int_1^{e^6}{\frac{1}{6x}dx}=1$$

$$\int_1^{e^6}{\frac{1}{6x}dx} = \frac{1}{6}ln(x) |_1^{e^6} = \frac{1}{6}ln(e^6) - \frac{1}{6}ln(1)=\frac{1}{6}\times6 - \frac{1}{6}\times 0 = 1 - 0 = 1$$

**Yes f(x) is a probability density function on the interval $[1, e^6]$ **
